Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-01-31 Journal1/paper2TNSM/pr.tex
reach reviewer 2 questions

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of the O-RU and the Fronthaul Capacity}
Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to all the UEs served by it. From \eqref{eq2}, the power of each O-RU $r$ is obtained as follows, 
%{\color{red} is this the sum rate of all users?}
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}\label{cr}
C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
\subsection{Mean Delay}
In this part, the end-to-end mean delay for each service is obtained.
Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,
T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}. 
%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$). 
The propagation delay is the time takes for a signal to reach its destination. It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the capacity of the link). The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
Also, the transmission delay is the amount of time required to push all the packets into the fiber link.
Moreover, it can formulated as 
$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the sum-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean arrival data rate of each link.
So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we ignore the other two delays for simplification;
So, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$).
%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
%T^{\text{\text{tot}}} \approx T^{\text{proc}}
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
Since, by using Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
where $M_s^{d}$, $M_s^{c}$ and 
$M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively. 
Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have 
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$  
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.

@@

In this method, PRB and power are dynamically allocated. The number of VNFs is obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm \ref{alg1} (GAA algorithm ) for O-RU assignment.}

>>>>

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{s}^{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of the O-RU and the Fronthaul Capacity}
Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to all the UEs served by it. From \eqref{eq2}, the power of each O-RU $r$ is obtained as follows, 
%{\color{red} is this the sum rate of all users?}
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
\end{equation}
Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}\label{cr}
C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
\end{equation}
where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
\subsection{Mean Delay}
In this part, the end-to-end mean delay for each service is obtained.
Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,
\begin{subequations}
\begin{alignat}{4}
T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}. 
\end{alignat}
\end{subequations}
%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$). 
The propagation delay is the time takes for a signal to reach its destination. It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the propagation speed of the link). The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
Also, the transmission delay is the amount of time required to push all the packets into the fiber link.
Moreover, it can formulated as 
$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the data-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean packet size transmitting in each link.
So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.

\textcolor{magenta}{ We can reduce the complexity of our delay calculation and enhance the performance of our solution by eliminating propagation and transmission delays to focus on obtaining the optimal number of VNF. 
In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed for simplification;
Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km. Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}. so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $. Since, fronhaul, midhaul and backhaul are fiber optics, c is the speed of light. Also, due to the use of the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced. But we do not focus on edge processing in this paper.
In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$. So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$. As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$. for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.  
}

So, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$). 
%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
%\begin{equation}
%T^{\text{\text{tot}}} \approx T^{\text{proc}}
%\end{equation}
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
Since, by using Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
\begin{equation}
\begin{split}
T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
\end{split}
\end{equation}
where $M_s^{d}$, $M_s^{c}$ and 
$M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively. 
Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{subequations}
\begin{alignat}{4}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
\end{alignat}
\end{subequations}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have 
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$  
%\begin{equation}
%\begin{split}
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
%\end{split}
%\end{equation}

\textcolor{violet}{Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard. Solving the problem is complex. To solve the problem by inspiring Stackelberg, we reformulate the equation \eqref{c16} to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader). So, the new problem has two variables of power and PRB assignment. This new problem is convex by relaxing the binary variable (PRB assignment) and can be solved by the Lagrangian function. After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.}

@@

In this method, PRB and power are dynamically allocated. The number of VNFs is obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm \ref{alg1} (GAA algorithm ) for O-RU assignment.
The figures in \cite{lee2018dynamic} show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area. We will also see that our proposed algorithm performs better than FBDR in the next subsection.
